---
title: "p8105_hw1_yl4358"
author: "YI LIU"
date: "9/17/2019"
output: github_document
---

# Problem 1

```{r problem1}
library(tidyverse)

set.seed(1)
first_df = tibble(
  sample = rnorm(8),
  vec_log = sample > 0,
  vec_char = c("My", "name", "is", "YI", "LIU", "and", "study", "biostatistics"),
  vec_factor = factor(c("high", "medium", "low", "high", "medium", "low", "low", "low"))
)

```

The mean of the sample is `r mean(pull(first_df, sample))`

The mean of vec_log is `r mean(pull(first_df, vec_log))`

We cannot take the mean of character vector and factor vector.


```{r pb1_convert_var_type}
as.numeric(pull(first_df, vec_log)) * pull(first_df, sample)
as.factor(pull(first_df, vec_log)) * pull(first_df, sample)
as.numeric(as.factor(pull(first_df, vec_log))) * pull(first_df, sample)

```


# Problem 2

```{r problem 2}
second_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_log2 = (x + y) > 1,
  vec_num = as.numeric(vec_log2),
  vec_factor = as.factor(vec_log2)
)

```

* The dataset has `r nrow(second_df)` rows and `r ncol(second_df)` columns

* The mean, median and standard deviation of x is `r mean(pull(second_df, x))`, `r median(pull(second_df, x))`, `r sd(pull(second_df, x))`

* The proportion of cases for which x + y > 1 is `r sum(pull(second_df, vec_num))/length(pull(second_df, vec_num))`


```{r yx_scatter}
ggplot(second_df, aes(x = x, y = y, color = "y vs x")) + geom_point()
ggsave("hw1_plot1_yl4358.pdf")
ggplot(second_df, aes(x = x, y = vec_num, color = "vec_num vs x")) + geom_point()
ggplot(second_df, aes(x = x, y = vec_factor, color = "vec_factor vs x")) + geom_point()
```






